The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
filling out the discussion

The fibre fringing is another example of how test spectra that are
unusual from the training set can be projected as peculiar artefacts in the
label space.  In other words, unusual spectra can appear as `clumps' in
regions of parameter space that we could consider as being normal 
(e.g., Solar-type stars).  We addressed this issue for the main-sequence
and giant models by using a joint model to calculate relative weights.
However, spectra that are unusual from the joint model training set can
still project as systematic artefacts.  An interrogation of our results
has identified one such group of metal-poor ($[{\rm Fe/H}] \approx -0.4$)
stars near $\teff \approx 3250$~K, which peculiarly sit above the isochrone. 
The \rave\ morphological classifications \citep{Matijevic_2012} indicate 
these stars have chromospheric emission, a feature not present in our 
training set.  Based on this (and other previously discussed) examples,
we recommend either a thorough investigation of unexpected structure
\footnote{Before submitting to \emph{Nature}} 
using all the available 
information from \rave, or judicious quality controls (e.g., requiring the 
morphological classification to be `normal') to remove these spurious measurements.

\stub{weird projections in the data space --> use morphological classifications to guide}

\stub{quality constraints, etc}

\stub{despite limitations, this catalog may be useful for science. N of abundances}

\stub{in the future we will do spectrophotometric distances to improve on this}

This catalog constitutes the largest collection of stellar abundances for stars in the
first \gaia\ data release.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \project{unRAVE} catalog will help advance understanding 
of the Milky Way's formation and evolution.

>>>>

The fibre fringing is another example of how test spectra that are
unusual from the training set can be projected as peculiar artefacts in the
label space.  In other words, unusual spectra can appear as `clumps' in
regions of parameter space that we could consider as being normal 
(e.g., Solar-type stars).  We addressed this issue for the main-sequence
and giant models by using a joint model to calculate relative weights.
However, spectra that are unusual from the joint model training set can
still project as systematic artefacts.  An interrogation of our results
has identified one such group of metal-poor ($[{\rm Fe/H}] \approx -0.4$)
stars near $\teff \approx 3250$~K, which peculiarly sit above the isochrone. 
The \rave\ morphological classifications \citep{Matijevic_2012} indicate 
these stars have chromospheric emission, a feature not present in our 
training set.  Based on this (and other previously discussed) examples,
we recommend either a thorough investigation of unexpected structure\footnote{
Before submitting to \emph{Nature}} 
using all the available 
information from \rave, or judicious quality controls (e.g., requiring the 
morphological classification to be `normal') to remove these spurious projections.

\stub{based on our interrogation of the data, we supply a 'QC' column that uses very strict requirements to eliminate weird things: morphological classifications, SNR, R (pipeline), $\chi_r^2$, etc....}

We have presented the largest collection of stellar abundances for stars in the 
first \gaia\ data release.  In total more than X.XX million abundances are
available, with effective temperature $\teff$, surface gravity $\logg$ and 
metallicity available for XXXXXX stars.  Despite the caveats and limitations 
discussed here, our validation experiments and comparisons with high-resolution
spectroscopic studies suggests that our results have sufficient accuracy and
precision to be useful for exoplanet host stars studies 
\citep[c.f.,][]{Valenti_Fischer_2005}, investigations of the Milky Way disk 
\citep[c.f.,][]{Reddy_2003,Reddy_2006,Bensby_2014}, and a multitude of 
chemo-dynamic studies.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \project{unRAVE} catalog will help advance understanding 
of the Milky Way's formation and evolution.
